### 2025-03-18 writing/manuscript.tex
figures update

\begin{table}[H]
  \centering
  \begin{threeparttable}
  \caption{Distribution of referrals by area}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
  \toprule
  Area & Only one referral & Both areas & Total \\
  \midrule
  Verbal & 65 & 608 & 673 \\
  Math & 61 & 608 & 669 \\
  \midrule
  Total & 126 & 1,216 & 1,342 \\
  \bottomrule
  \end{tabular*}
  \begin{tablenotes}[flushleft]
  \footnotesize
  \item[] \textit{Note:} The table shows how many referrers made referrals in only one area versus both areas. "Only one referral" indicates individuals who made referrals exclusively in that area. "Both areas" shows individuals who made referrals in both verbal and math areas. The majority of referrers (608) made referrals in both areas.
  \end{tablenotes}
  \label{tab:referral_distribution}
  \end{threeparttable}
\end{table}

\begin{table}[H]
  \centering
  \begin{threeparttable}
  \caption{Summary statistics for network members by nomination status}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccc}
  \toprule
  & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
  \cmidrule{2-3} \cmidrule{4-5}
  & Not Referred & Referred & Not Referred & Referred \\
  \midrule
  Reading z-score & 0.070 & 0.509 & 0.079 & 0.465 \\
  & (0.003) & (0.039) & (0.003) & (0.040) \\
  [1ex]
  Math z-score & 0.079 & 0.452 & 0.087 & 0.590 \\
  & (0.003) & (0.042) & (0.003) & (0.043) \\
  [1ex]
  GPA z-score & -0.066 & 0.705 & -0.069 & 0.711 \\
  & (0.003) & (0.041) & (0.003) & (0.041) \\
  [1ex]
  Tie strength z-score & -0.153 & 2.690 & -0.184 & 2.488 \\
  & (0.003) & (0.091) & (0.003) & (0.090) \\
  [1ex]
  Low-SES & 0.334 & 0.374 & 0.338 & 0.384 \\
  & (0.001) & (0.019) & (0.001) & (0.019) \\
  [1ex]
  Med-SES & 0.515 & 0.513 & 0.513 & 0.507 \\
  & (0.001) & (0.019) & (0.001) & (0.019) \\
  [1ex]
  High-SES & 0.151 & 0.113 & 0.149 & 0.109 \\
  & (0.001) & (0.012) & (0.001) & (0.012) \\
  [1ex]
  Female & 0.524 & 0.562 & 0.520 & 0.428 \\
  & (0.001) & (0.019) & (0.001) & (0.019) \\
  [1ex]
  Age & 20.945 & 20.501 & 20.961 & 20.490 \\
  & (0.006) & (0.104) & (0.006) & (0.099) \\
  \midrule
  Observations & 128,174 & 673 & 127,481 & 669 \\
  \bottomrule
  \end{tabular*}
  \begin{tablenotes}[flushleft]
  \footnotesize
  \item[] \textit{Note:} Standard errors in parentheses. GPA, test scores, and tie strength are standardized at the network level. For each referrer's network, we first calculated the mean and standard deviation of each measure. We then computed the average of these means and standard deviations across all referrers. Each individual's score was standardized using these network-level statistics. The standardization formula is $z = (x - \bar{x}_{network}) / \sigma_{network}$, where $\bar{x}_{network}$ and $\sigma_{network}$ are the average of network means and standard deviations, respectively. Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively. Tie strength measures the number of connections between individuals.
  \end{tablenotes}
  \label{tab:stats_by_nomination}
  \end{threeparttable}
\end{table}

@@

\begin{figure}[H]
  \centering
  \caption{Top decile performer share across the sample, network and referals }\label{topdecile}
  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/top_decile_comparison.png}
  \begin{tablenotes}
    \footnotesize
    \item[] \textit{Note:} This figure displays the percentage share of individuals across three dimensions. First bar shows referrers in the top decile for math and reading based on admin data. Second bar is the share of top decile in their networks. Third column shows the share of top decile among the referrals made. We test differences between proportions across these three groups using two-sample tests of proportions. For both math and reading scores, the differences between Sample and Network ($p<0.001$), Sample and Referrals ($p<0.005$), and Network and Referrals ($p<0.001$) are all statistically significant.
  \end{tablenotes}
\end{figure}

@@

  \begin{figure}[H]
    \centering
    \caption{Baseline Referral Patterns by SES}
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_tie_strength.png}
        \caption{Referral Rates}
        \label{fig:tie_ses}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_tie_strength.png}
        \caption{Academic Performance of Referrals}
        \label{fig:tie_topses}
    \end{subfigure}
    \label{fig:tie_combinedses}
    \caption*{\footnotesize\textit{Note:} The left panel shows the availability of SES groups across socioeconomic strata. The right panel shows the availability of top decile performers within each SES group.}
  \end{figure}

@@

  \begin{figure}[H]
    \centering
    \caption{Baseline Referral Patterns by SES}
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_rates.png}
        \caption{Referral Rates}
        \label{fig:baseline_rates}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_performance.png}
        \caption{Academic Performance of Referrals}
        \label{fig:baseline_performance}
    \end{subfigure}
    \label{fig:baseline_combined}
    \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across socioeconomic strata in the baseline condition. The right panel shows the average standardized math and reading scores of referred students by referrer's SES.}
  \end{figure}

  \begin{figure}[H]
    \centering
    \caption{Treatment Effects on Referral Patterns}
    \label{fig:treat_combined}
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_treatment_effects.png}
        \caption{Changes in Referral Rates}
        \label{fig:treat_rates}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/treatment_effect.png}
        \caption{Changes in Academic Performance of Referrals}
        \label{fig:treat_performance}
    \end{subfigure}
    \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline). The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Treatment Effects on Tie Strength}
  \label{fig:treat_combined2}
  \begin{subfigure}[t]{0.49\textwidth}
      \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_ties.png}
      \caption{Changes in Referral Rates}
      \label{fig:tietreat_rates}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.49\textwidth}
      \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ties_treatment_effects.png}
      \caption{Changes in Academic Performance of Referrals}
      \label{fig:tietreat_performance}
  \end{subfigure}
  \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline). The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
\end{figure}

  \begin{table}[H]
    \caption{SES shares by SES and referral status}
    \centering
    \begin{tabular}{lcccc}
    \hline
    & \multicolumn{2}{c}{Baseline} & \multicolumn{2}{c}{Bonus} \\
    \cline{2-5}
    & Not Referred & Referred & Not Referred & Referred \\
    \hline
    Low-SES & 0.361 & 0.473 & 0.368 & 0.531 \\
    Middle-SES & 0.527 & 0.583 & 0.515 & 0.520 \\
    High-SES & 0.201 & 0.180 & 0.193 & 0.286 \\
    \hline
    Observations & 131,777 & 699 & 123,878 & 643 \\
    \hline
    \end{tabular}
    \label{tab:social_class_nominations_combined}
 \end{table}

%  \begin{table}[H]
%   \caption{SES shares by academic measure}
%   \centering
%   \begin{tabular}{lcccc}
%   \hline
%   & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
%   \cline{2-5}
%   & Referred & Top Decile & Referred & Top Decile \\
%   \hline
%   Low-SES & 0.495 & 0.301 & 0.505 & 0.318 \\
%   Middle-SES & 0.562 & 0.460 & 0.541 & 0.445 \\
%   High-SES & 0.207 & 0.239 & 0.254 & 0.237 \\
%   \hline
%   Observations & 275 & 385 & 283 & 355 \\
%   \hline
%   \end{tabular}
%   \label{tab:ses_shares_by_measure}
%   \end{table}

\begin{table}[H]
  \caption{SES shares in Verbal}
  \centering
  \begin{tabular}{lcccc}
  \hline
  & Top Decile & Availability & \multicolumn{2}{c}{Referred} \\
  \cline{4-5}
  & & & Baseline & Bonus \\
  \hline
  Low-SES & 0.301 & 0.398 & 0.483 & 0.508 \\
  Middle-SES & 0.460 & 0.438 & 0.595 & 0.527 \\
  High-SES & 0.239 & 0.282 & 0.161 & 0.259 \\
  \hline
  Observations & 385 & 25,196 & 147 & 128 \\
  \hline
  \end{tabular}
  \label{tab:ses_shares_verbal}
  \end{table}

  \begin{table}[H]
  \caption{SES shares in Math}
  \centering
  \begin{tabular}{lcccc}
  \hline
  & Top Decile & Availability & \multicolumn{2}{c}{Referred} \\
  \cline{4-5}
  & & & Baseline & Bonus \\
  \hline
  Low-SES & 0.318 & 0.398 & 0.464 & 0.554 \\
  Middle-SES & 0.445 & 0.428 & 0.570 & 0.512 \\
  High-SES & 0.237 & 0.278 & 0.200 & 0.310 \\
  \hline
  Observations & 355 & 23,883 & 153 & 130 \\
  \hline
  \end{tabular}
  \label{tab:ses_shares_math}
  \end{table}

    \begin{table}[H]
      \caption{Verbal performance (z-score) of Referred Students}
      \centering
      \begin{tabular}{lccc}
      \hline
      & Baseline & Bonus & Total \\
      \hline
      Low-SES & 0.644 & 0.383 & 0.513 \\
      Middle-SES & 0.551 & 0.509 & 0.530 \\
      High-SES & 0.705 & 0.820 & 0.763 \\
      \hline
      Observations & 351 & 322 & 673 \\
      \hline
      \end{tabular}
      \label{tab:performance_verbal}
      \end{table}

      \begin{table}[H]
      \caption{Math performance (z-score) of Referred Students }
      \centering
      \begin{tabular}{lccc}
      \hline
      & Baseline & Bonus & Total \\
      \hline
      Low-SES & 0.560 & 0.483 & 0.521 \\
      Middle-SES & 0.683 & 0.647 & 0.665 \\
      High-SES & 0.921 & 0.836 & 0.879 \\
      \hline
      Observations & 348 & 321 & 669 \\
      \hline
      \end{tabular}
      \label{tab:performance_math}
      \end{table}

>>>>

\begin{table}[H]
  \centering
  \begin{threeparttable}
  \caption{Distribution of referrals by area}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccc}
  \toprule
  Area & Only one referral & Both areas & Total \\
  \midrule
  Verbal & 65 & 608 & 673 \\
  Math & 61 & 608 & 669 \\
  \midrule
  Total & 126 & 1,216 & 1,342 \\
  \bottomrule
  \end{tabular*}
  \begin{tablenotes}[flushleft]
  \footnotesize
  \item[] \textit{Note:} The table shows how many referrers made referrals in only one area versus both areas. ``Only one referral'' indicates individuals who made referrals exclusively in that area. ``Both areas'' shows individuals who made referrals in both verbal and math areas. The majority of referrers (608) made referrals in both areas.
  \end{tablenotes}
  \label{tab:referral_distribution}
  \end{threeparttable}
\end{table}

\begin{table}[H]
  \centering
  \begin{threeparttable}
  \caption{Summary statistics for network members by nomination status}
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccc}
  \toprule
  & \multicolumn{2}{c}{Verbal} & \multicolumn{2}{c}{Math} \\
  \cmidrule{2-3} \cmidrule{4-5}
  & Not Referred & Referred & Not Referred & Referred \\
  \midrule
  Reading z-score & 0.070 & 0.509 & 0.079 & 0.465 \\
  & (0.003) & (0.039) & (0.003) & (0.040) \\
  [1ex]
  Math z-score & 0.079 & 0.452 & 0.087 & 0.590 \\
  & (0.003) & (0.042) & (0.003) & (0.043) \\
  [1ex]
  GPA z-score & -0.066 & 0.705 & -0.069 & 0.711 \\
  & (0.003) & (0.041) & (0.003) & (0.041) \\
  [1ex]
  Tie strength z-score & -0.153 & 2.690 & -0.184 & 2.488 \\
  & (0.003) & (0.091) & (0.003) & (0.090) \\
  [1ex]
  Low-SES & 0.334 & 0.374 & 0.338 & 0.384 \\
  & (0.001) & (0.019) & (0.001) & (0.019) \\
  [1ex]
  Med-SES & 0.515 & 0.513 & 0.513 & 0.507 \\
  & (0.001) & (0.019) & (0.001) & (0.019) \\
  [1ex]
  High-SES & 0.151 & 0.113 & 0.149 & 0.109 \\
  & (0.001) & (0.012) & (0.001) & (0.012) \\
  % [1ex]
  % Female & 0.524 & 0.562 & 0.520 & 0.428 \\
  % & (0.001) & (0.019) & (0.001) & (0.019) \\
  % [1ex]
  % Age & 20.945 & 20.501 & 20.961 & 20.490 \\
  % & (0.006) & (0.104) & (0.006) & (0.099) \\
  \midrule
  Observations & 128,174 & 673 & 127,481 & 669 \\
  \bottomrule
  \end{tabular*}
  \begin{tablenotes}[flushleft]
  \footnotesize
  \item[] \textit{Note:} Standard errors in parentheses. GPA, test scores, and tie strength are standardized at the network level. For each referrer's network, we first calculated the mean and standard deviation of each measure. We then computed the average of these means and standard deviations across all referrers. Each individual's score was standardized using these network-level statistics. The standardization formula is $z = (x - \bar{x}_{network}) / \sigma_{network}$, where $\bar{x}_{network}$ and $\sigma_{network}$ are the average of network means and standard deviations, respectively. Low-SES, Med-SES, and High-SES are binary variables indicating the share of participants in estrato 1 and 2, 3 and 4, or 5 and 6, respectively. Tie strength measures the number of connections between individuals.
  \end{tablenotes}
  \label{tab:stats_by_nomination}
  \end{threeparttable}
\end{table}

@@

\begin{figure}[H]
  \centering
  \caption{Effect of the Bonus on Referrals}
  \begin{subfigure}[t]{0.7\textwidth}
    \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/reading_combined.png}
      \caption{Reading}  
      \label{fig:reading_combined}
  \end{subfigure}
  \begin{subfigure}[t]{0.7\textwidth}
    \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/math_combined.png}
      \caption{Math}
      \label{fig:math_combined}
  \end{subfigure}
  \label{fig:both_combined}
  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions. We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$). The bottom panel shows the average standardized math and tie strength of referrals across conditions. We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$). For both math and reading, referred students }
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Top decile performer share across the sample, network and referals }\label{topdecile}
  \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/top_decile_comparison.png}
  \begin{tablenotes}
    \footnotesize
    \item[] \textit{Note:} This figure displays the percentage share of top decile individuals according to the admin data across three dimensions. First bar shows referrers in the sample of participants. Second bar is the share of top decile individuals in their networks. Third column shows the share of top decile among the referrals made. We test differences between proportions across these three groups using two-sample tests of proportions. For both math and reading scores, the differences between Sample and Network ($p<0.001$), Sample and Referrals ($p<0.005$), and Network and Referrals ($p<0.001$) are all statistically significant.
  \end{tablenotes}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \caption{Participant network composition by SES}
  \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/z_ses_tie_strength.png}
  \label{fig:tie_ses}
  \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES. We test differences in standardized tie strength across SES groups using two-sample $t$-tests. All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$). The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero. These patterns reveal strong homophily in network formation, particularly among High SES students, while Low SES students show moderate homophily patterns.}
\end{figure}

%   \begin{figure}[H]
%     \centering
%     \caption{Baseline Referral Patterns by SES}
%     \begin{subfigure}[t]{0.49\textwidth}
%         \centering
%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_tie_strength.png}
%         \caption{Referral Rates}
%         \label{fig:tie_ses}
%     \end{subfigure}
%     \hfill
%     \begin{subfigure}[t]{0.49\textwidth}
%         \centering
%         \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_top_tie_strength.png}
%         \caption{Academic Performance of Referrals}
%         \label{fig:tie_topses}
%     \end{subfigure}
%     \label{fig:tie_combinedses}
%     \caption*{\footnotesize\textit{Note:} The left panel shows the availability of SES groups across socioeconomic strata. The right panel shows the availability of top decile performers within each SES group.}
%   \end{figure}

@@

% \begin{figure}[H]
%   \centering
%   \caption{Participant network composition by SES}
%   \includegraphics[width=\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/combined_baseline.png}
%   \label{fig:baseline_combined}
%   \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES. We test differences in z-score tie strength across SES groups using two-sample $t$-tests. All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$). The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero. These patterns reveal strong homophily in network formation, particularly among High SES students, while Low SES students show moderate homophily patterns.}
% \end{figure}

  \begin{figure}[H]
    \centering
    \caption{Baseline Referral Patterns by SES}
    \begin{subfigure}[t]{0.49\textwidth}
      \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_referral_distribution.png}
        \caption{Referral Rates}  
        \label{fig:baseline_rates}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\textwidth}
      \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_performance.png}
        \caption{Referral Performance}
        \label{fig:baseline_performance}
    \end{subfigure}
    \label{fig:baseline_combined}
    \caption*{\footnotesize\textit{Note:} The left panel shows the distribution of referrals across SES in the baseline condition. We test differences in SES shares across SES groups using two-sample tests of proportions. All differences are statistically significant ($p < 0.1$). The right panel shows the average standardized math and reading scores of referred students by referrer's SES. We test differences in z-scores across SES groups using two-sample $t$-tests and find no statistically significant differences in reading scores across SES groups (all $p > 0.36$). For math scores, we observe marginally significant differences between Low and High SES students ($p = 0.08$) and between Middle and High SES students ($p = 0.18$), with High SES referring peers with higher math performance.}
  \end{figure}

  \begin{figure}[H]
    \centering
    \caption{Effect of the Bonus}
    \label{fig:treat_combined}
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_treatment_effects.png}
        \caption{Changes in Referral Rates}
        \label{fig:treat_rates}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.49\textwidth}
        \centering
        \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/treatment_effect.png}
        \caption{Changes in Referral Performance}
        \label{fig:treat_performance}
    \end{subfigure}
    \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across SES. We test differences in SES shares across conditions using two-sample tests of proportions. For Low-SES, only the change in referral share of Middle-SES is statistically significant ($p = 0.034$). For Middle-SES, only the change in referral share of High-SES is statistically significant ($p = 0.027$). For High-SES, only the change in referral share of Middle-SES is statistically significant ($p = 0.059$). The right panel shows the differences in math and reading z-scores across SES. We test differences in SES shares across conditions using two-sample $t$-tests. For both reading and math scores, the only statistically significant difference is in the reading scores for Low-SES ($p = 0.026$).}
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Effect of the Bonus on Tie Strength}
  \label{fig:treat_combined2}
  \begin{subfigure}[t]{0.49\textwidth}
      \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/baseline_ties.png}
      \caption{Changes in Referral Rates}
      \label{fig:tietreat_rates}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.49\textwidth}
      \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ties_treatment_effects.png}
      \caption{Changes in Referral Performance}
      \label{fig:tietreat_performance}
  \end{subfigure}
  \caption*{\footnotesize\textit{Note:} The left panel shows the changes in referral rates across socioeconomic strata (bonus minus baseline). The right panel shows the differences in average standardized math and reading scores of referred students by referrer's SES.}
\end{figure}
